---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sccthemes

<!-- badges: start -->
<!-- badges: end -->

The goal of sccthemes is to provide a consistent styling framework and helper functions for graphics made in ggplot at the Suffolk County Council.

This package has been heavily inspired by [bbplot](https://github.com/bbc/bbplot), the BBC's R package for creating and exporting graphics made in ggplot.

## Installation

You can install the development version of sccthemes from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thomaszwagerman/sccthemes")
```

## Suffolk County Council 
The font and colour codes have been sourced from the [Suffolk County Council's website](https://www.suffolk.gov.uk/), and Google Chrome's Inspect functionality (Ctrl + Shift + i).

The style can be called to any ggplot2 object using `scc_style()`

```{r style_example, warning = FALSE, message = FALSE}
library(ggplot2)
library(gapminder)
library(dplyr)
library(sccthemes)

barchart_data <- gapminder |> 
  filter(year == 2007 & continent == "Europe") |> 
  arrange(desc(gdpPercap)) |> 
  head(5)

barchart_data |> 
  ggplot(aes(x = country, y = gdpPercap)) +
  geom_bar(
    stat = "identity",
    position = "identity",
    color = "#333333",
    fill = "#428bca"
  ) +
  geom_hline(
    yintercept =  0,
    size = 1,
    colour = "#333333"
  ) +
  scc_style() +
  labs(
    title = "Europe's Richest Countries",
    subtitle = "GDP per Capita, 2007"
  )
```

## Helper functions for ggplot2
Helper functions for certain types of plots are also provided in this repo.

Instead of the code above for instance, this package also contains helper functions which are rough and ready:

```{r helper_example, warning = FALSE, message = FALSE}
library(ggplot2)
library(gapminder)
library(dplyr)
library(sccthemes)

barchart_data <- gapminder |> 
  filter(year == 2007 & continent == "Europe") |> 
  arrange(desc(gdpPercap)) |> 
  head(5)

scc_barchart(
  barchart_data,
  x = "country",
  y = "gdpPercap",
  title = "Europe's Richest Countries",
  subtitle = "GDP per Capita, 2007"
)

```
Currently, there are helper functions for the following plot types:

- Barplots
- Piecharts (but why you [should discourage their use if you can](https://www.data-to-viz.com/caveat/pie.html))

The BBC's ["ggplot cookbook"](https://bbc.github.io/rcookbook/#make_a_bar_chart) is a good starting point to use as a reference.

More helper functions will be added as I need to make them.

## Future additions to this package
If there is a further need in the future, other styling options can be added.

For example:

- [bslib](https://rstudio.github.io/bslib/) themes for Shiny, see this example from [UKCEH](https://github.com/NERC-CEH/UKCEH_shiny_theming).
- gt table themes
